Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-25 proposal/amr-bio.tex
proposal\amr-bio.tex Upgraded to bibLaTeX to automatically put erratum in...

\documentclass[11pt]{article}
\usepackage{fullpage,times,url}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Closely Related Publications}

\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung
  Tai. ``Discrete Quantum Theories.'' In \emph{J. Phys. A: Math. Theor.},
  \textbf{47}, 2014.

\item Andrew J. Hanson, Gerardo Ortiz, Amr Sabry, and Yu-Tsung Tai,
  ``Geometry of Discrete Quantum Computing.'' In \emph{J. Phys. A:
  Math. Theor.}, \textbf{46}, 2013.

\item Juliana K. Vizzotto, Andr\'e Rauber Du Bois, and Amr Sabry, ``The Arrow
  Calculus as a Quantum Programming Language,'' In the \emph{Workshop on Logic,
  Language, Information and Computation}, 2009.

\item Thorsten Altenkirch, Jonathan Grattage, Juliana K. Vizzotto, and Amr
  Sabry, ``An Algebra of Pure Quantum Programming.'' In the \emph{Workshop on
  Quantum Programming Languages}, 2005. Final version in the \emph{Electronic
  Notes in Theoretical Computer Science}, vol. 170, pp. 23-47, 2007.

\item Juliana K. Vizzotto, Thorsten Altenkirch, and Amr Sabry, ``Structuring
  Quantum Effects: Superoperators as Arrows.''  \emph{Mathematical Structures
    in Computer Science} (MSCS), Volume 16, Issue 03, pages 453-468, June
  2006.

\end{enumerate}

>>>>

\documentclass[11pt]{article}
\usepackage{fullpage,times,url}
\usepackage[utf8]{inputenc}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=5,doi=false,isbn=false,url=false}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nocite{DQT2014, geometry2013, VDS2009, AGVS2005, VAS2006}
\printbibliography[title={Closely Related Publications}]
